---
title: "R Notebook"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    df_print: paged
    fig_caption: yes
    theme: paper
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

# EDA
```{r load_data, include = FALSE}
library(MASS)
library(data.table)
library(tidyverse)
library(corrplot)
library(gridExtra)
library(ggthemes)
library(caret)
library(randomForest)
library(party)
library(rpart)
library(rpart.plot)
load("data/falls.RData")
load("data/methwick.RData")
load("data/vitals.RData")
```

```{r names_falls}
names(falls)

```

```{r names_methwick}
names(methwick)
```

```{r dim_falls}
dim(falls)
```

```{r dim_methwick}
dim(methwick)
```

```{r str_falls}
str(falls)
```

```{r str_methwick}
str(methwick)
```

```{r summary_falls}
summary(falls)
```

```{r summary_methwick}
summary(methwick)
```

```{r hours_falls}
summary(chron::hours(falls$Fall_Time))
```
```{r}
x <- chron::hours(falls$Fall_Time)
y <- runif(length(x))
boxplot(y ~ x)
```

```{r}
h <- hist(chron::hours(falls$Fall_Time), breaks = seq(0, 24, by = 1), col = "darkgray", border = "black", main = "Proportion of Times")
rug(chron::hours(falls$Fall_Time))
```

```{r}
str(h)
```
```{r}
plot(h, col = heat.colors(length(h$mids))[length(h$count)-rank(h$count)+1], ylim = c(0, max(h$count)+5), main="Falls through Time by hour", sub="Counts shown above bar, actual values shown with rug plot")
rug(chron::hours(falls$Fall_Time))
text(h$mids, h$count, h$count, pos=3)
rm(h)
```

```{r fall_injuries_wrangling, include = FALSE}
falls_injuries <- read.csv(file = "data/falls_injuries.csv", header = FALSE)
falls_injuries$severity <- rowSums(falls_injuries[, 4:104])
colnames(falls_injuries)[colnames(falls_injuries) == 'V1'] <- 'id'
colnames(falls_injuries)[colnames(falls_injuries) == 'V2'] <- 'date'
colnames(falls_injuries)[colnames(falls_injuries) == 'V3'] <- 'time'
hist(falls_injuries$severity)
fall_severity <- data.frame(falls_injuries$severity)
colnames(fall_severity)[colnames(fall_severity) == 'falls_injuries.severity'] <- 'severity'
fall_severity$severity[fall_severity$severity >= 1] <- 1
falls <- bind_cols(falls, fall_severity)
```

```{r falls_notes_wranglign, include = FALSE}
fn <- read_lines("data/fall_notes.txt")
fall_notes <- as.data.frame(substr(fn, start = 1, stop = 7), stringsAsFactors = T)
colnames(fall_notes) <- "ID"
fall_notes$date <- substr(fn, start = 7, stop = 17)
fall_notes$time <- substr(fn, start = 18, stop = 27)
fall_notes$notes <- substr(fn, start = 28, stop = 110000)
save(fall_notes, file = "data/fall_notes.RData")
```

```{r vitals_wrangling, include = FALSE}
vit <- vitals
setDT(vit)
vit$newid <- paste(vit$ID, vit$Date, vit$Time, sep = " | ")
vit$newnumber <- paste(vit$Number, vit$Number2, sep = " | ")
vit <- vit[, c("Date","ID", "Time", "Notes", "Number", "Number2"):=NULL]
vit <- reshape(vit, idvar = "newid", timevar = "Vital_Code", direction = "wide")
vit$ID <- substr(vit$newid, 1, 4)
vit$date <- substr(vit$newid, 7, 17)
vit$time <- substr(vit$newid, 20, 33)
vit$ID <- as.integer(vit$ID)
vit$ID <- trimws(vit$ID)
vit$date <- trimws(vit$date)
vit$date <- lubridate::as_date(vit$date)
vit$time <- trimws(vit$time)
vit$time <- chron::times(vit$time, format =  "h:m:s")
vit$bloodpressure <- vit$`newnumber.BP        `
vit$oxygen <- vit$`newnumber.OXYGEN    `
vit$pain <- vit$`newnumber.PAIN      `
vit$pulse <- vit$`newnumber.PULSE     `
vit$resp <- vit$`newnumber.RESP      `
vit$temp <- vit$`newnumber.TEMP      `
vit$weight <- vit$`newnumber.WEIGHT    `
vit$height <- vit$`newnumber.HEIGHT    `
vit$spo2 <- vit$`newnumber.SPO2 DEL  `
vit$intake <- vit$`newnumber.INTAKE    `
vit$bloodsugar <- vit$`newnumber.BLOODSUG  `
vit$fluids <- vit$`newnumber.~FLUIDRES `
vit$output <- vit$`newnumber.OUTPUT    `


vit <- subset(vit, select=-c(`newnumber.BP        `,
`newnumber.OXYGEN    `,
`newnumber.PAIN      `,
`newnumber.PULSE     `,
`newnumber.RESP      `,
`newnumber.TEMP      `,
`newnumber.WEIGHT    `,
`newnumber.HEIGHT    `,
`newnumber.SPO2 DEL  `,
`newnumber.INTAKE    `,
`newnumber.BLOODSUG  `,
`newnumber.~FLUIDRES `,
`newnumber.OUTPUT    `))

vit <- data.frame(lapply(vit, gsub, pattern = "|", replacement = "", fixed = TRUE))
vit <- data.frame(lapply(vit, trimws))
vit$bloodpressure[vit$bloodpressure == ""] <- NA
vit$oxygen[vit$oxygen == ""] <- NA
vit$pain[vit$pain == ""] <- NA
vit$pulse[vit$pulse == ""] <- NA
vit$resp[vit$resp == ""] <- NA
vit$temp[vit$temp == ""] <- NA
vit$weight[vit$weight == ""] <- NA
vit$height[vit$height == ""] <- NA
vit$spo2[vit$spo2 == ""] <- NA
vit$intake[vit$intake == ""] <- NA
vit$bloodsugar[vit$bloodsugar == ""] <- NA
vit$fluids[vit$fluids == ""] <- NA
vit$output[vit$output == ""] <- NA

vit$ID <- trimws(vit$ID)
vit$date <- trimws(vit$date)
vit$date <- lubridate::as_date(vit$date)
vit$time <- trimws(vit$time)
vit$time <- chron::times(vit$time, format =  "h:m:s")

vit$month <- lubridate::month(vit$date)
vit$day <- lubridate::day(vit$date)
vit$year <- lubridate::year(vit$date)
vit$hour <- chron::hours(vit$time)

falls$month <- lubridate::month(falls$Fall_Date)
falls$day <- lubridate::day(falls$Fall_Date)
falls$year <- lubridate::year(falls$Fall_Date)
falls$hour <- chron::hours(falls$Fall_Time)

## add date of fall
```

```{r}
fall_notes$date <- trimws(fall_notes$date)
fall_notes$date <- as.Date(fall_notes$date, "%m/%d/%Y")
fall_notes$time <- trimws(fall_notes$time)
fall_notes$time <- chron::times(fall_notes$time, format = "h:m:s")

fall_notes$month <- lubridate::month(fall_notes$date)
fall_notes$day <- lubridate::day(fall_notes$date)
fall_notes$year <- lubridate::year(fall_notes$date)
fall_notes$hour <- chron::hours(fall_notes$time)

vit$ID <- as.integer(vit$ID)
vit <- vit[ , !(names(vit) %in% c("newid"))]
fall_notes <- fall_notes[ , !(names(fall_notes) %in% c("date", "time"))]
falls_complete <- right_join(vit, falls)
fall_notes$ID <- trimws(fall_notes$ID)
fall_notes$ID <- as.integer(fall_notes$ID)
falls_complete <- right_join(fall_notes, falls_complete)
```

```{r facility_location, include = FALSE}
f <- read_lines("data/facility_info.txt")
facility_loc <- as.data.frame(substr(f, start = 1, stop = 3), stringsAsFactors = T)
colnames(facility_loc) <- "Type"
facility_loc$Unit <- substr(f, start = 4, stop = 12)
facility_loc$ID <- substr(f, start = 12, stop = 30)
facility_loc$ID <- trimws(facility_loc$ID)
methwick$facility <- facility_loc$Type[match(methwick$id, facility_loc$ID)]
```

```{r prof_notes_wrangling, include = FALSE}
p <- read_lines("data/profile_notes.txt")
prof_notes <- as.data.frame(substr(p, start = 1, stop = 6), stringsAsFactors = T)
colnames(prof_notes) <- "id"
prof_notes$conditions <- substr(p, start = 7, stop = 107)
prof_notes$history <- substr(p, start = 107, stop = 400)
prof_notes$conditions <- trimws(prof_notes$conditions)
prof_notes$history <- trimws(prof_notes$history)
prof_notes$id <- trimws(prof_notes$id)
prof_notes$conditions[prof_notes$conditions == ""] <- NA
prof_notes$conditions[prof_notes$conditions == "N/A"] <- NA
prof_notes$history[prof_notes$history == ""] <- NA
prof_notes$history[prof_notes$history == "N/A"] <- NA

prof_notes$dementia[grepl("dement", tolower(prof_notes$conditions)) == TRUE |
                    grepl("dement", tolower(prof_notes$history)) == TRUE] <- 1

prof_notes$dementia[(grepl("dement", tolower(prof_notes$conditions)) == FALSE &
                    is.na(prof_notes$conditions) == FALSE) |
                    (grepl("dement", tolower(prof_notes$history))== FALSE &
                    is.na(prof_notes$history) == FALSE)] <- 0

prof_notes$alzheimers[grepl("alzhe", tolower(prof_notes$conditions)) == TRUE |
                    grepl("alzhe", tolower(prof_notes$history)) == TRUE] <- 1

prof_notes$alzheimers[(grepl("alzhe", tolower(prof_notes$conditions)) == FALSE &
                    is.na(prof_notes$conditions) == FALSE) |
                    (grepl("alzhe", tolower(prof_notes$history))== FALSE &
                    is.na(prof_notes$history) == FALSE)] <- 0

prof_notes$copd[grepl("copd", tolower(prof_notes$conditions)) == TRUE |
                    grepl("copd", tolower(prof_notes$history)) == TRUE] <- 1

prof_notes$copd[(grepl("copd", tolower(prof_notes$conditions)) == FALSE &
                    is.na(prof_notes$conditions) == FALSE) |
                    (grepl("copd", tolower(prof_notes$history))== FALSE &
                    is.na(prof_notes$history) == FALSE)] <- 0

prof_notes$diabetes[grepl("diabe", tolower(prof_notes$conditions)) == TRUE |
                    grepl("diabe", tolower(prof_notes$history)) == TRUE] <- 1

prof_notes$diabetes[(grepl("diabe", tolower(prof_notes$conditions)) == FALSE &
                    is.na(prof_notes$conditions) == FALSE) |
                    (grepl("diabe", tolower(prof_notes$history))== FALSE &
                    is.na(prof_notes$history) == FALSE)] <- 0

prof_notes$hypertension[grepl("hyperte", tolower(prof_notes$conditions)) == TRUE |
                    grepl("hyperte", tolower(prof_notes$history)) == TRUE] <- 1

prof_notes$hypertension[(grepl("hyperte", tolower(prof_notes$conditions)) == FALSE &
                    is.na(prof_notes$conditions) == FALSE) |
                    (grepl("hyperte", tolower(prof_notes$history))== FALSE &
                    is.na(prof_notes$history) == FALSE)] <- 0

```

```{r data_merge_notes, include = FALSE}
methwick$dementia <- prof_notes$dementia[match(methwick$id, prof_notes$id)]
methwick$alzheimers <- prof_notes$alzheimers[match(methwick$id, prof_notes$id)]
methwick$copd <- prof_notes$copd[match(methwick$id, prof_notes$id)]
methwick$diabetes <- prof_notes$diabetes[match(methwick$id, prof_notes$id)]
methwick$hypertension <- prof_notes$hypertension[match(methwick$id, prof_notes$id)]

falls_comp <- falls_complete %>%
  mutate(id = tolower(ID))
falls_complete2 <- merge(falls_comp, methwick, by = "id")
eda <- falls_complete2
```

## what does the fall distribution  between sexes look like?
```{r}
bar <- eda %>%
  dplyr::select(sex, has_fallen) %>%
  group_by(sex) %>%
  summarise(n = n())

ggplot(bar, aes(x = sex, y = n)) +
  geom_bar(stat = "identity")
```
## what does the age range distribution look like?
```{r}
agerange <- eda %>%
  dplyr::select(sex, age_group) %>%
  group_by(age_group) %>%
  summarise(n = n())

ggplot(agerange, aes(x = age_group, y = n)) +
  geom_bar(stat = "identity")
```
Seems to correlate with what we would expect

## What does it look like side by side? This plot reinforces the previous two
```{r}
sexagerange <- eda %>%
  dplyr::select(sex, age_group) %>%
  group_by(age_group, sex) %>%
  summarise(n = n())

ggplot(sexagerange, aes(x = age_group, y = n, fill = factor(sex))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "sex", breaks = c("F","M"), labels = c("F", "M")) +
  theme(legend.position = "bottom")
```
This is what we would expect

## Do women just fall more frequently? Controlling for unique(id)
```{r}
sexageidrange <- eda %>%
  dplyr::select(sex, age_group, id) %>%
  group_by(age_group, sex, id) %>%
  summarise(n = n())

ggplot(sexageidrange, aes(x = sex, y = n)) +
  geom_point(aes(color = sex))

# x <- sexageidrange
# x$sex <- factor(x$sex)
# x$color[x$sex == "M"] <- "blue"
# x$color[x$sex == "F"] <- "red"
# dotchart(x$n, labels = x$id, cex = .7, groups = x$sex, gcolor = "black", color = x$color)
# remove(x)
```
looks like men have a great occurence of multiple falls and a higher number

## of the fallers how many have been documented to have dementia?
```{r}
eda %>%
  filter(dementia == 1) %>%
  group_by(id) %>%
  summarise(n = n())
```

## of the fallers how many have been documented to have copd?
```{r}
eda %>%
  filter(copd == 1) %>%
  group_by(id) %>%
  summarise(n = n())
```

## of the fallers how many have been documented to have diabetes?
```{r}
eda %>%
  filter(diabetes == 1) %>%
  group_by(id) %>%
  summarise(n = n())
```

## of the fallers how many have been documented to have alzheimers?
```{r}
eda %>%
  filter(alzheimers == 1) %>%
  group_by(id) %>%
  summarise(n = n())
```

## of the fallers how many have been documented to have hypertension?
```{r}
eda %>%
  filter(hypertension == 1) %>%
  group_by(id) %>%
  summarise(n = n())
```

## what is the distribution of the time fallers fall?
```{r}
hist(x = chron::hours(eda$time), breaks = 24)
```
Looks like 1-3 are big hours, likely coming back from lunch or these are areas of activity

## what day of the week do people fall?
```{r}
wdayhist <- eda %>%
  dplyr::select(id, Fall_Date) %>%
  mutate(fall_date = lubridate::wday(Fall_Date)) %>%
  group_by(fall_date) %>%
  summarise(n = n())

ggplot(wdayhist, aes(x = fall_date, y = n)) +
  geom_bar(stat = "identity")
```
Sunday is the biggest day for falls. Church?


## which facility are fallers located in?
```{r}
x <- eda %>%
  dplyr::select(id, facility) %>%
  group_by(facility) %>%
  summarise(n = n())

ggplot(x, aes(x = facility, y = n)) +
  geom_bar(stat = "identity")
```

## What does the population look like?
```{r}
methwick %>%
  dplyr::select(id, has_fallen, sex) %>%
  group_by(sex) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = sex, y = n)) +
  geom_bar(stat = "identity")
```
## What about fallers and non-fallers in those populations?
```{r}
methwick %>%
  dplyr::select(has_fallen, sex) %>%
  group_by(has_fallen, sex) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = sex, y = n, fill = factor(has_fallen))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "has_fallen", breaks = c("TRUE","FALSE"), labels = c("TRUE", "FALSE")) +
  theme(legend.position = "bottom")
```

## adjusting for facility = NA, what does the current resident population look like?
```{r}
methwick %>%
  filter(is.na(facility) == FALSE) %>%
  dplyr::select(has_fallen, sex) %>%
  group_by(has_fallen, sex) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = sex, y = n, fill = factor(has_fallen))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "has_fallen", breaks = c("TRUE","FALSE"), labels = c("TRUE", "FALSE")) +
  theme(legend.position = "bottom")
```

## How many people are currently residents?(where facility is not na)
```{r}
methwick %>%
  filter(is.na(facility) == FALSE) %>%
  summarise(n = n())
```

## fallers and non-fallers by age group
```{r}
methwick %>%
  dplyr::select(has_fallen, age_group) %>%
  group_by(has_fallen, age_group) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = age_group, y = n, fill = factor(has_fallen))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "has_fallen", breaks = c("TRUE","FALSE"), labels = c("TRUE", "FALSE")) +
  theme(legend.position = "bottom")
```

## adjusting for people who have a facility=NA which may indicate a non-resident
```{r}
methwick %>%
  filter(is.na(facility) == FALSE) %>%
  dplyr::select(has_fallen, age_group) %>%
  group_by(has_fallen, age_group) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = age_group, y = n, fill = factor(has_fallen))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "has_fallen", breaks = c("TRUE","FALSE"), labels = c("TRUE", "FALSE")) +
  theme(legend.position = "bottom")
```
## adjusting for people who have a facility=NA and a mobility impairment
```{r}
methwick %>%
  filter(is.na(facility) == FALSE) %>%
  dplyr::select(has_fallen, mobility_impairment) %>%
  group_by(has_fallen, mobility_impairment) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = mobility_impairment, y = n, fill = factor(has_fallen))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_discrete(name = "has_fallen", breaks = c("TRUE","FALSE"), labels = c("TRUE", "FALSE")) +
  theme(legend.position = "bottom")
```

```{r, include = FALSE}
set.seed(666)
eda$severity[eda$To_Hospital == "Y"] <- 1

readr::write_csv(eda, path = "eda.csv")
```

# histogram of severity
```{r}
hist(eda$severity)
```
# 4 Plots corresponding to the GLM for has_fallen data, classifying predictions
```{r, warnings = FALSE}

eda$dementia[is.na(eda$dementia) == TRUE] <- 0
eda$alzheimers[is.na(eda$alzheimers) == TRUE] <- 0
eda$copd[is.na(eda$copd) == TRUE] <- 0
eda$diabetes[is.na(eda$diabetes) == TRUE] <- 0
eda$hypertension[is.na(eda$hypertension) == TRUE] <- 0

lmfit <- glm(data = eda, has_fallen ~ day + age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + age_group + dementia + alzheimers + hypertension, family = "binomial")

lmfit_data <- methwick %>%
  dplyr::select(has_fallen = has_fallen,
         age = age,
         age_group = age_group,
         sex = sex,
         race = race,
         pacemaker = pacemaker,
         visual_impairment = visual_impairment,
         mobility_impairment = mobility_impairment,
         bmi = bmi,
         dementia = dementia,
         alzheimers = alzheimers,
         copd = copd,
         diabetes = diabetes,
         hypertension = hypertension)
lmfit_data$dementia[is.na(lmfit_data$dementia) == TRUE] <- 0
lmfit_data$alzheimers[is.na(lmfit_data$alzheimers) == TRUE] <- 0
lmfit_data$copd[is.na(lmfit_data$copd) == TRUE] <- 0
lmfit_data$diabetes[is.na(lmfit_data$diabetes) == TRUE] <- 0
lmfit_data$hypertension[is.na(lmfit_data$hypertension) == TRUE] <- 0

lmfit <- glm(data = lmfit_data, has_fallen ~ age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + dementia + alzheimers + copd + diabetes + hypertension, family = "binomial")

plot(lmfit)
```
# Summary of has_fallen fit data
```{r}
lmfit2 <- glm(data = lmfit_data, has_fallen ~ age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + dementia + alzheimers + diabetes + hypertension, family = "binomial")

summary(lmfit2)
```



## Testing just the diagnostic varaibles

- wanted to assess the viability of just the clinical diagnostics by themseslves.  Similar results.  

```{r}
lmfit3 <- glm(data = lmfit_data, has_fallen ~ alzheimers + diabetes + hypertension, family = "binomial")

summary(lmfit3)
```

# Summary of 70% glm training data
```{r}
# Create a df with 80% of data
set.seed(666)
index <- sample(nrow(lmfit_data), 0.70*nrow(lmfit_data), replace = F)
lmfit_training <- lmfit_data[index,]
lmfit_test <- lmfit_data[-index,]
# Fit the training model
lmfit_train <- glm(data = lmfit_training, 
             has_fallen ~ age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + dementia + alzheimers + copd + diabetes + hypertension + 0, 
             family = binomial(link = "logit"), control = list(maxit = 100))
summary(lmfit_train)
lmfit_train$xlevels[["race"]] <- union(lmfit_train$xlevels[["race"]], levels(lmfit_test$race))
lmfit_train$xlevels[["pacemaker"]] <- union(lmfit_train$xlevels[["pacemaker"]], levels(lmfit_test$pacemaker))
lmfit_predict <- predict(lmfit_train, lmfit_test, type="response")
```
# Summary of glm fit data for has_fallen testing data
```{r}
lmfit_testing <- glm(data = lmfit_test, 
             has_fallen ~ age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + dementia + alzheimers + copd + diabetes + hypertension + 0, 
             family = binomial(link = "logit"), control = list(maxit = 100))
summary(lmfit_testing)
```
# Summary of the prediction data for testing data
```{r}
summary(lmfit_predict)
```
# Plot to show divergence for predict non_factored has_fallen data
```{r}
plot(lmfit_predict)
```
#anova description of training data with Chi Squared test
```{r}
anova(lmfit_train, test = "Chisq")
```
# Accuracy
```{r}
lmfit_test$has_fallen <- as.character(lmfit_test$has_fallen)
lmfit_test$has_fallen[lmfit_test$has_fallen==FALSE] <- "0"
lmfit_test$has_fallen[lmfit_test$has_fallen==TRUE] <- "1"
lmfit_results <- predict(lmfit_train,newdata=lmfit_test,type='response')
classification_errors <- mean(lmfit_results != lmfit_test$has_fallen)
print(paste('Logistic Regression Accuracy',1-classification_errors))
```
# Confusion matrix for has_fallen
```{r}
print("Confusion Matrix for Logistic Regression"); table(lmfit_test$has_fallen, lmfit_results > 0.5)
```
# Odds Ratios for has_fallen data
```{r, warning=FALSE}
exp(cbind(OR=coef(lmfit_train), confint(lmfit_train)))
```

# Severity Ctree

```{r}
# tree <- ctree(has_fallen~has_fallen ~ age + sex + race + pacemaker + visual_impairment + mobility_impairment + bmi + dementia + alzheimers + copd + diabetes + hypertension , lmfit_training)
# plot(tree, type = 'simple')

fall_tree <- party::ctree(severity ~ month + day + age + sex + race + pacemaker + visual_impairment + mobility_impairment + dementia + alzheimers + copd + diabetes + hypertension , data = eda)
summary(fall_tree)
plot(fall_tree, type = 'simple')
```

```{r}
# test_tree <- rpart(factor(severity) ~ year + age + sex + race + pacemaker + visual_impairment + mobility_impairment , data = eda)
set.seed(666)
eda_recode <- eda
# eda_recode$severity_split[eda$severity == 1] <- 0
# eda_recode$severity_split[eda$severity >= 2] <- 1
index <- sample(nrow(eda_recode), 0.80*nrow(eda_recode), replace = F)
training <- eda_recode[index,]
testing <- eda_recode[-index,]
```

# Odds ratio and histogram of the prediction relating to severity
```{r}
# Fit the training model
trained <- glm(data = training, 
             severity ~ month + day + age + sex + race + pacemaker + visual_impairment + Prior_Physical + mobility_impairment, family = binomial(link = "logit"), control = list(maxit = 100))
summary(trained)

trained$xlevels[["race"]] <- union(trained$xlevels[["race"]], levels(testing$race))
trained$xlevels[["pacemaker"]] <- union(trained$xlevels[["pacemaker"]], levels(testing$pacemaker))
prediction <- predict(trained, testing, type="response")
table(testing$severity, prediction > 0.5)
tpred <- predict(trained, training, type = "response")
table(training$severity, tpred > 0.5)
hist(prediction)
exp(cbind(OR=coef(trained), confint(trained)))
```

# rpart tree for severity data, non-factored
```{r}
test_tree <- rpart(severity ~ month + age + sex + race + pacemaker + visual_impairment + mobility_impairment , data = eda)
par(xpd = TRUE)
rpart.plot(test_tree, compress = TRUE)
dtree.pred <- predict(test_tree, testing, type = "vector")
dtree.perf <- table(testing$severity, dtree.pred, dnn=c("Actual", "Predicted"))
dtree.perf
```
# Summary and histograms for the test_tree and severity data
```{r}
summary(test_tree)
rpart.plot(test_tree)

summary(eda$severity)
hist(eda$severity)
```